\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
% -----------------------------------
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue,
  linkbordercolor={0 0 1}
}
% -----------------------------------
\usepackage[
    backend=biber,
    style=alphabetic,]
    {biblatex}
\addbibresource{citation.bib}
% -----------------------------------
\title{Zotero Tutorial: \LaTeX\ Examples}
\author{Ryan Sh\`iji\'e D\`u}
\date{\today}
% -----------------------------------
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.1in}
% -----------------------------------
\begin{document}
\input{command.tex}

\maketitle

With 
\href{https://retorque.re/zotero-better-bibtex/}{Better BibTeX}
and 
\href{https://github.com/wshanks/Zutilo}{Zutilo}, we can obtain the correct \texttt{.bib} entries, \verb|\cite{...}| command, and the formatted citation from simple shortcuts. 

For example, I could cite these entries about the tears of wine \cite{DuklerEtAl_20, PhysicsGirl_19}. The first is a journal article and the second is a video. If one wants to share this paper with collaborator via email say, then it would be convenient to be able to obtain a formatted citation quickly. And this is possible as well:\vspace*{2mm}\\
\;\hspace*{1cm}
\begin{minipage}{.85\textwidth}
    Dukler, Y., Ji, H., Falcon, C., Bertozzi, A.L., 2020. Theory for undercompressive shocks in tears of wine. Physical Review Fluids 5, 34002. https://doi.org/10.1103/PhysRevFluids.5.034002
\end{minipage}

Our ``pipeline'' preserves special characters. For example, the \"o in the title of this paper is printed in the References section correctly \cite{Vanneste_21}; as well as the accents in the author names of this paper \cite{Caspar-CohenEtAl_21}.

Let's cite some things others than journal articles. This is conference paper \cite{Diamantakis_14}, this is a book chapter \cite{Buhler_14b} from the book \cite{Buhler_14}, and this is a patent \cite{TERANEtAl_18}. Here we cite the thesis and a presentation by the same author \cite{Shakespeare_15,Shakespeare_21}. The citation for the presentation could be better. This is likely because presentation is categorized as \verb|@misc| in the \texttt{.bib} file. 

Automation is great, but we should still be careful about the details. For example, this data is not cited well \cite{cisl_rda_ds633.3}. The recommended citation for this data product is:\vspace*{2mm}\\
\;\hspace*{1cm}
\begin{minipage}{.85\textwidth}%
European Centre for Medium-Range Weather Forecasts (2019): ERA5 Reanalysis (0.25 Degree Latitude-Longitude Grid). Research Data Archive at the National Center for Atmospheric Research, Computational and Information Systems Laboratory. Dataset. https://doi.org/10.5065/BH6N-5N20. Accessed† dd mmm yyyy.
\end{minipage}%

\section{Live Demonstration}
\cite{ChienCramer_22, MaxianDonev_22}

Chien, S.Y., Cramer, M.S., 2022. Compressible high-pressure lubrication flows in thrust bearings. Journal of Fluid Mechanics 939. https://doi.org/10.1017/jfm.2022.240

Maxian, O., Donev, A., 2022. Slender body theories for rotating filaments. arXiv:2203.12059 [math-ph, physics:physics].




\newpage
\printbibliography


\end{document}
